% !TEX root =  ../main.tex
\section{Representing Processes via Semantic Roles}

A portion of the grade science exams test the ability to recognize the instances of physical, biological, and other natural processes. 
The questions present a short description of an instance and multiple process names as the answer choices. 

Table below shows a few examples:
\\
\fbox{

\begin{minipage}{17em}

1) As water vapor rises in the atmosphere, it cools and changes back to liquid.
Tiny drops of liquid form clouds in this process called (A) condensation (B) evaporation (C) precipitation (D) run-off.\\

2) The process of change from an egg to an adult butterfly is an example of: (A) vibrations (B) metamorphosis.\\

3) A new aluminum can made from used cans is an example of: (A) recycling (B) reducing (C) reusing (D) repairing	

\end{minipage}
}
\\
\\
The descriptions of the instances are often short. 
They mention the main entities involved and the change brought about by the process. 
At the 4th grade level, the questions do not involve deep knowledge about the sub-events or their sequential order.
Rather the questions test for shallower knowledge about the entities undergoing change, the resulting artifacts, and the main characteristic action describing the process. 
This knowledge is naturally expressed via semantic roles. 
Accordingly we design a simple representation that encodes information about each process via the following roles:
\begin{enumerate}[noitemsep, nolistsep]
\item {\em Input} -- This role captures the main input to the process or the object undergoing the process. e.g., Water is an input to the evaporation process. 
\item {\em Result} -- The artifact that results from the process or the change that results from the process e.g., Water vapor is a result of evaporation. 
\item {\em Trigger} -- The main action, expressed as a verb or its nominalization, indicating the occurrence of the process. e.g., {\em converted} is a trigger for evaporation.
\item {\em Enabler} -- The artifact, condition or action that enables the process to happen. e.g., {\em Sun} is a heat source that is enabler for evaporation.
\end{enumerate}

Our goal is to build aggregate knowledge about processes from multiple sentences. 
If effect we wish to create a table, whose columns are the semantic roles and rows are role fillers obtained from sentences mentioning the process.
We gather knowledge about processes from both definitional sentences and from sentences that describe instances of the processes. 

Definitional sentences present {\em type} information about the roles. 
For instance, the input to evaporation is typically a liquid. 
During question answering, we have to check type compatibility of the roles in the question and the definitional sentence. 
Having instance level information in the process knowledge can help situations where type resolution fails. 
On the other hand, having definitional sentences provides better coverage of information about roles compared to instance sentences,
which can sometimes omit roles that are obvious. 


\input{body/mate}
\input{body/domain-adaptation}
\input{body/distant-supervision}



